---
title: "Original Homework code"
author: "Frank Azorsa"
date: "9/16/2019"
output:
  html_document:
    toc: true
    toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

***
#Introduction to the Assigment # 2
***

This is the code for [Homework 02](https://fuzzyatelin.github.io/bioanth-stats/homework-02.html), on week three of AN597. This is homework associated with Modules [6](https://fuzzyatelin.github.io/bioanth-stats/module-06/module-06.html), [7](https://fuzzyatelin.github.io/bioanth-stats/module-07/module-07.html) and [8](https://fuzzyatelin.github.io/bioanth-stats/module-08/module-08.html).

####The first question asks:

>Every Saturday morning, at the same time, a primatologist goes and sits in the forest to listen for titi monkey calls, counting the number of calls they hear in a 2 hour window from 5am to 7am. Based on previous knowledge, she believes that the mean number of calls she will hear in that time is exactly 15. Let X represent the appropriate Poisson random variable of the number of calls heard in each monitoring session.

***
###Question 1:
#####What is the probability that she will hear more than 8 calls during any given session?
***

```{r}
ppois (8, lambda = 15, lower.tail = FALSE)
```
+ Answer:

***
###Question 2:
#####What is the probability that she will hear no calls in a session?
***

```{r}
dpois(x=0, lambda = 15)
```

***
###Question 3:
#####What is the probability that she will hear exactly 3 calls in a session?
***

```{r}
dpois(x=3, lambda =15)
```

***
###Question 4:
#####Plot the relevant Poisson mass function over the values in range 0 ≤ x ≤ 30.
***

```{r}
rv <- 0:30
fs <- ppois (rv, lambda =15)
plot (rv, fs, type ="s", xlab = "Calls", ylab = "Distribution Function")
```
```{r}
ys <- 0:30
fs <- dpois (ys,lambda = 15)
plot(ys, fs, xlab = "Calls", ylab = "Pr(X-x)", main = "Probability Mass Function")
```
```{r}
x <- 0:30
l = 15
probset<- dpois (x=x,lambda = 1)
barplot(probset,names.arg=x,space = 0,xlab = "x", ylab="Pr(X-x)", main="Probability Mass Function")
```

***
###Question 5:
#####Simulate 104 results from this distribution (i.e., 2 years of Saturday monitoring sessions).

***
```{r}
sim <-rpois(104, lambda = 15)
sim
summary(sim)
```

***
###Question 6:
#####Plot the simulated results using hist() and use xlim() to set the horizontal limits to be from 0 to 30. How does your histogram compare to the shape of the probability mass function you plotted above?
***

```{r}
hist(sim, xlim = c(0,30), main = "Histogram of the simulation", col = "white", xlab = "number of calls")
```
